Towards detecting critical crowd density with Wi-Fi positioning: Case Amsterdam ArenA

### 2016-08-03 PaperOnSmoothing/draft-31052016.tex
Continued writing the Positioning section.

The positions of smart phones are reconstructed using received signal strength (RSS) values and methods similar to multi-lateration. 
The method is based on the decrease of signal strength when the distance between transmitter and receiver increases.
Using a model for the decrease, the distance between transmitter and receiver can be reconstructed from the received signal strength.
When we have at least three such reconstructed distances, the position of a transmitter can be uniquely determined using the method of circular lateration [ref: Kushki et al.].\\
The path loss model is the Friis equation, given by
\begin{equation}
P_{R}=P_{T}+10\lambda\log_{10}(\frac{c}{4\pi fr})
\end{equation}
where we use $\lambda=2$ (line of sight condition), $c$ is the speed of light, $f$ is 2.4 GHz, and $r$ is the distance between the position $(x,y)$ (in two dimensions) of the mobile device and the position $(x_{i},y_{i})$ of router $i$, given by 
\begin{equation}
r=\sqrt{((x-x_{i})^2+(y-y_{i})^2)}
\end{equation}
Received signal strengths of packets captured at different sensors are grouped in time to constitute separate `measurements'. 
To estimate positions from these groups of measurements (signal strengths) a chi-square data fit is performed.\\

The uncertainties associated with the chi-square fits are given by the covariance matrix, which is the inverse of the matrix of second-order derivatives of the chi-square function.
The values in the covariance matrix give the uncertainty in the parameters that corresponds to a $1\sigma$ error or an increase of $\chi^2+1$.

>>>>

The positions of smart phones are reconstructed using received signal strength (RSS) values and methods similar to multi-lateration. 
The method is based on the decrease of signal strength when the distance between transmitter and receiver increases.
Using a model for the decrease, the distance between transmitter and receiver can be reconstructed from the received signal strength.
When we have at least three such reconstructed distances, the position of a transmitter can be uniquely determined using the method of circular lateration [ref: Kushki et al.].\\
The path loss model is the Friis equation, given by
\begin{equation}
P_{R}=P_{T}+10\lambda\log_{10}(\frac{c}{4\pi fr})
\label{friis}
\end{equation}
where we use $\lambda=2$ (line of sight condition), $c$ is the speed of light, $f$ is 2.4 GHz, and $r$ is the distance between the position $(x,y)$ (in two dimensions) of the mobile device and the position $(x_{i},y_{i})$ of router $i$, given by 
\begin{equation}
r=\sqrt{((x-x_{i})^2+(y-y_{i})^2)}
\end{equation}
Received signal strengths of packets captured at different sensors are grouped in time to constitute separate measurements. 
To estimate positions from these groups of measurements a chi-square data fit is performed.
The chi-square function is minimized by setting
\begin{equation}
\frac{d\chi^2}{dp}=0
\end{equation}
The uncertainties associated with the chi-square fits are calculated using the covariance matrix of the measurements.
If we assume Gaussian distributed measurements, the covariance matrix is the inverse of the matrix of second-order derivatives of the chi-square function, i.e.
\begin{equation}
C_{ij}^{-1}=\frac{1}{2}\frac{\partial^2\chi^2}{\partial p_{i}\partial p_{j}}
\end{equation}
The uncertainties in the parameters are obtained using a Taylor expansion of the nonlinear path loss function (Equation \ref{friis}).
The values of the uncertainty that correspond to a $1\sigma$ error or an increase of $\chi^2+1$ are given by the projection matrix
\begin{equation}
P=HCH^\top
\end{equation}
where $H$ is a matrix consisting of (first-order) partial derivatives of the path loss model with respect to the fit parameters.
The $1\sigma$ errors form the input to the smoothing method of the density estimation discussed in this paper.
